Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2016-08-10 Docs/IJES/journal.tex
Response: We included an explanation in the paper (at the end of Section 5.1) as follows: “The TO was defined based on previous empirical tests, where a larger TO (e.g., 5000 seconds) did not produce substantial differences in the experimental results.

All experiments were conducted on an otherwise idle Intel Core i$7$-$2600$ ($8$-cores), with $3$.$4$ GHz and $24$ GB of RAM, running Ubuntu $64$-bits. Each time was measured $3$ times (average taken). Based on standard deviation and tolerance interval to each set of time sample, it was obtained a statistical confidence of $91.7$\% to ESBMC (sequential, SS, PB and $\nu$Z), $95.9$\% to ESBMC-PS, and $92.0$\% to ILP and GA. A timeout condition (TO) is reached when the verification time is longer than $3600$ seconds. A memory-out (MO) occurs when the tool reaches $15$ GB of memory. The TO was defined based in previous empiric tests, where a bigger TO (5000 seconds, for example) do not caused difference in the results.

>>>>

All experiments were conducted on an otherwise idle Intel Core i$7$-$2600$ ($8$-cores), with $3$.$4$ GHz and $24$ GB of RAM, running Ubuntu $64$-bits. Each time was measured $3$ times (average taken). Based on standard deviation and tolerance interval to each set of time sample, it was obtained a statistical confidence of $91.7$\% to ESBMC (sequential, SS, PB and $\nu$Z), $95.9$\% to ESBMC-PS, and $92.0$\% to ILP and GA. A timeout condition (TO) is reached when the verification time is longer than $3600$ seconds. A memory-out (MO) occurs when the tool reaches $15$ GB of memory. \textcolor{blue}{The TO was defined based on previous empirical tests, where a larger TO ({\it e.g.}, $5000$ seconds) did not produce substantial differences in the experimental results.}
